Enrich the datasets with new columns.

### 2020-08-23 inst/analysis/analysis_stable.Rmd
Classification

---
title: "Empirical Evaluation of eval in R"
output:
  rmdformats::readthedown:
        code_folding: hide
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
    data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.5/deduplicated_more_calls.fst"
    #data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced-all.1/calls.fst"
    # The trace data on all CRAN does not have all the columns of the smaller corpus. The analysis will fail for the big corpus.

@@

source("inc/latextags.R")
create_tags(path("/var/lib/R/project-evalR/revalstudy/data", "analysisStable.tex"), prefix="", default=TRUE)
```

@@

```{r group_expr_resolved_functions}
group_expr_resolved_functions <- expr_resolved_call_arg %>%
                            mutate(function_expr2 = groupify_function(expr_resolved_function)) %>%
                            mutate(group_function_expr = fct_collapse(function_expr2, 
                              assignment = c("<-", "[[<-", "[<-", "$<-", "<<-", "="),
                              read = c("[", "[[", "$"),
                              parsing = c("parse", "str2lang", "str2expression", "parse_only", "base::parse"),
                              defusing = c("quote", "substitute", "bquote", "expr", "quo"),
                              expressions = c("as.list", "expression", "as.name", "as.expression", "list", "c", "as.data.frame", "as.character", "{", "modify_lang"),
                              calling = c("call", "as.call", "do.call"),
                              environment = c("environment", "as.environment"),
                              classAssign = c("@<-"),
                              classRead = c("slot", "@"),
                              classDef = c(".Primitive(\"class\")"),
                              logical = c("<", ">", "is.element"),
                              choice = c("if"),
                              anonymous = c("anonymous"),
                              primitive = c("primitive"),
                              function_meta = c("sys.calls", "function", "body", "missing"),
                              formula = c("~", "deriv", "D", "model.frame", "rootftfunc", "contest.lmerModLmerTest", "JacFunc", "gamlss.family", "contest1D.lmerModLmerTest", "contestMD.lmerModLmerTest", "reexpr"),                           
                              other_level = "other" ))
```

@@

>>>>

---
title: "Empirical Evaluation of eval in R"
output:
  rmdformats::readthedown:
        code_folding: hide
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
        self_contained: no
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
    data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.5/summarized-packages.fst"
    #data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced-all.1/calls.fst"
    # The trace data on all CRAN does not have all the columns of the smaller corpus. The analysis will fail for the big corpus.

@@

source("inc/latextags.R")
create_tags(path("/var/lib/R/project-evalR/revalstudy/inst/data", "analysisStable.tex"), prefix="", default=TRUE)
```

@@

```{r group_expr_resolved_functions}
group_expr_resolved_functions <- expr_resolved_call_arg %>%
                            mutate(function_expr2 = groupify_function(expr_resolved_function)) %>%
                            mutate(group_function_expr = fct_collapse(function_expr2, 
                              assignment = c("<-", "[[<-", "[<-", "$<-", "<<-", "=", "@<-"),
                              slot_access = c("[", "[[", "$", "slot", "@", "::", ":::"),
                              parsing = c("parse", "str2lang", "str2expression", "parse_only", "base::parse"),
                              defusing = c("quote", "substitute", "bquote", "expr", "quo"),
                              expressions = c("as.list", "expression", "as.name", "as.expression", "list", "c", "as.data.frame", "as.character", "{", "modify_lang"),
                              calling = c("call", "as.call", "do.call"),
                              environment = c("environment", "as.environment"),
                              logical = c("!", "&", "|", "&&", "||"),
                              relation = c("<", ">", "is.element", "<=", "=>", "!="),
                              choice = c("if"),
                              anonymous = c("anonymous"),
                              primitive = c("primitive"),
                              function_meta = c("sys.calls", "function", "body", "missing"),
                              arithmetic = c("+", "-", "*", "/", "%%", "^"),
                              formula = c("~", "deriv", "D", "model.frame", "rootftfunc", "contest.lmerModLmerTest", "JacFunc", "gamlss.family", "contest1D.lmerModLmerTest", "contestMD.lmerModLmerTest", "reexpr"),                           
                              other_level = "other" ))
```

@@

Another interesting figure is the degreee of polymorphism of the `expr` argument: how many different types (for `expr_resolved`) are there for one call sites?

```{r polymorphism_callsite}
expr_resolved_polymorphism <- eval_calls %>% group_by(eval_call_srcref) %>%
        summarise(polym_degree = vec_unique_count(expr_resolved_type))

expr_resolved_monomorphic <- expr_resolved_polymorphism %>% filter(polym_degree == 1)
nb_monomorphic <- expr_resolved_monomorphic %>% nrow()
```

```{r polymorphism}
expr_resolved_polymorphism %>% ggplot() +
  geom_bar(aes(x = polym_degree)) +
  scale_x_continuous(breaks=c(0, 1, 5, 10)) +
  labs(title = "Degree of polymorphism", x = "degree", y = "n") 
```

`r nb_monomorphic` call sites are not polymorphic, which represents `r nb_monomorphic / nb_call_sites * 100`% of the call sites.

From the monomorphic functions, we can deduce how many are _replaceable_:

```{r}
expr_resolved_replaceable <- expr_resolved_monomorphic %>% left_join(eval_calls) %>% mutate(can_replace = map_lgl(expr_resolved,  is_replaceable_str))
```

### 2020-08-23 inst/analysis/enrich_dataset.Rmd
Classification

---
title: "Enrich the datasets with new columns."
output:
  rmdformats::readthedown:
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  data_dirpath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.5/"
  data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.5/calls.fst"
  data_kagglepath: "/var/lib/R/project-evalR/kaggle-korpus/run/titanic/calls.fst"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "html") })
---

>>>>

---
title: "Enrich the datasets with new columns."
output:
  rmdformats::readthedown:
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  data_dirpath: "/var/lib/R/project-evalR/run/package-evals-traced/"
  data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced/calls-final.fst"
  data_kagglepath: "/var/lib/R/project-evalR/kaggle-korpus/run/titanic/calls.fst"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "html") })
---
